Simple Wind Models

### 2010-07-10 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5033 ac11df5e-a788-c23b-a8e1-c758c323924d

\begin{abstract}
\begin{itemize}
\item Emission is a generic feature of (nearly) isotropic winds.  This
  emission fills in absorption at $v \approx 0$, significantly
  complicating the absorption-line analysis. 
\end{itemize}
\end{abstract}

@@

In this paper, we will focus on two sets of radiative transitions
associated with the Fe$^+$ and Mg$^+$ ions, a choice motivated by 
our own observations \citep{rubin10b}.  Although this is a limited
set, the two ions and their transitions have 
characteristics that resemble the properties for the majority of low-ions 
observed in cool-gas outflows. [wording still stinks] Therefore, many
of our results may be generalized to other studies.

The Mg$^+$ ion, with a single 3s electron in the ground-state,
exhibits an alkali doublet of transitions similar to the
\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
we present the energy level diagram for this 
\mgiid\ doublet.  In non-relativistic quantum
mechanics, the 2p$^6$3p level is said to be split by spin-orbit
coupling which produces the line doublet.  These are the only
\ion{Mg}{2} electric-dipole transitions 
with wavelengths near 2800\AA. Also, the transtion connecting
the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
selection rules.  Therefore, an absorption from
\maconfig~$\to$~\mbconfig\
is followed nearly 100$\%$ of the time by a spontaneous decay to the
ground state and our treatment will ignore any other possibilities
(e.g.\ absorption of a second photon).

The physics of the \mgiid\ doublet
is analagous to the physics of \ion{H}{1}
\lya, the \naid\ doublet, and many other doublets commonly
studied in the ISM and IGM.  These doublets differ only in
the transiton wavelengths and the energy of the doublet separation. 
For \ion{H}{1} \lya, the
separation is sufficiently small ($\Delta v = c \Delta E / E \approx
1.3 \mkms$) that most radiative transfer treatments actually ignore the fact that
there are two transitions.   This is generally a justifiable
assumption because 
most astrophysical processes have turbulent motions that
significantly exceed this velocity separation and effectively mix the
two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \, \mkms$),  
\ion{Na}{1} ($\Delta v \approx 304 \, \mkms$), and most of the other doublets
commonly studied the separations are large and the lines
must be treated separately.  Regarding analysis of outflows, the line
separation plays an important role when the outflow speed $\mvr
\gtrsim \Delta v$.

Iron exhibits the most complex set of energy levels of the elements
frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
energy levels recorded \citep{iron}, and even this is an
incomplete list.  
One reason for the complexity of iron is
that the majority of its configurations exhibit fine-structure splitting.
This includes the ground-state configuration (\aconfig) which is split
into 5 levels with 
excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
$T_{\rm ex} \approx 500-1500$\,K.  These levels are usually labelled by the total angular momentum
$J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
Transitions between these fine-structure levels are 
forbidden (magnetic-dipole) with spontaneous decay times of several hours.

In this paper, we will focus on transitions between the ground-state
configuration and the levels associated with the \zconfig\
configuration.  This set of transitions are named the
UV1 mutliplet with wavelengths near 2600\AA.
There are two resonance-line transitions (defined to originate in the
true ground-state) associated with this multiplet, \feiid,
corresponding to $\Delta J = 0, -1$.  The solid (green) downward
arrows in Figure~\ref{fig:energy} mark the transitions that connect to
the upper energy levels of the resonance lines.  These transitons can
occur following the absorption of a single photon by the ion in its
ground-state.

The Figure also shows (as dashed downward arrows) two of the
transitions that connect to higher energy levels of the \zconfig\
configuration.  Radiatively, these can only occur after the absorption
of two photons: one to raise the electron from the ground-state to an
excited state and one from the excited state to one of the \zconfig\
levels with $J \le 5/2$.  The excitation of the Fe$^+$ ion by the
absorption of UV photons is termed indirect UV pumping
\citep[e.g][]{sv02,pcb06} and requires the ion to lie
near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
following, we will assume that this does not occur and that only the 
true ground-state is populated by electrons.

Our calculations also ignore collisional
processes\footnote{Recombination is also ignored.}, i.e.\ collisional
excitation and de-excitation of the various levels.  For the
fine-structure levels of the \aconfig\ configuration, the excitation
energies are modest ($T_{\rm ex} \sim 1000$\,K) but the critical
density $n_c$ is very large.  For the \aconfig$_{9/2} \to
$\aconfig$_{7/2}$ transition, the critical density $n_c \approx XX
\cm{-3}$.  At these densities, one would predict significant (and
detectable) quantities of \ion{Fe}{1} which has not yet been observed
\citep[see also][]{pcb06}.  The strongest arguement for neglecting
collisions is the general absence of {\it absorption} from the
fine-structure levels of the \aconfig\ configuration.  [Does Kate see
blue-shifted FeII* in absorption?]  This provides an empirical
demonstration that collsioinal excitation is insignificant, and by
inference one may neglect collisional de-excitation.  Meanwhile, the
critical density and excitation energies for \ion{Mg}{2} are $n_c =
??, T_{\rm ex} \approx 50,000$\,K.

@@

Nearly all of the absorption studies on cool-gas outflows 
have focused on intensely, star-forming galaxies.  The
intrinsic emisison of these galaxies is a complex combination of
stars and \ion{H}{2} regions that is then modulated by dust and gas
within the galaxy's ISM.  In terms of the spectral regions studied
here, most stars show a featureless continuum with a few spectral
types showing significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
[Any emission??]  \ion{H}{2} regions, meanwhile, are observed to emit
at the \mgiid\ doublet, primarily due to recombinations in the outer
layers [How about FeII?].  It is beyond the scope of this paper to
properly model the 
stellar absorption and \ion{H}{2} region emission, but the reader
should be aware that they can complicate the observed spectrum,
independent of a galactic outflow.
In the following, we will simply assume a flat continuum 
normalized to unit value.  The size of the emitting
region $r_{\rm source}$, however, is a variable parameter.

@@

In this section, we explore a simple yet illustrative wind model for
a galactic-scale outflow.  The properties of this wind were tuned, in
part, to yield a \ion{Mg}{2} absorption profile 
simlar to that observed toward $z<1$, star-forming galaxies
\citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
favor this fiducial model over any other wind scenario nor are its
properties any more physically motivated. 
Its primary purpose is to establish a baseline for exploration.

@@

\begin{equation}
n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2}
\end{equation}
(mass-flux conserving) and a velocity law

\begin{equation}
v_r (r) = v_0 r
\end{equation}
which corresponds to a purely radial flow.  Turbulent motions are
characterized by a Doppler parameter $b_{\rm turb}$.  
The wind is isotropic, dust-free, and extends from an inner wind
radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  At
the center of the wind 
is a homogenous source of continuum photons with size $r_{\rm source}$.  Lastly,
we convert the hydrogen density $n_{\rm H}$ to the number density of
Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
absolute metallicity of 1/2 solar and depletion factors of 1/10 and
1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
and \nfe=\nmg/2.   
These normalizations give a wind with a peak optical depth $\tau
>> 1$ to \mgiia\ that becomes optically thin over a velocity range
spanning $v_r \approx 100 - 1000 \, \mkms$.  
All of the parameters are summarized in Table~\ref{tab:fiducial}.

In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
profiles against radius for the fiducial wind model;  
their single power-law expressions are evident.  The figure also
shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
This profile is what determines the observed absorption/emission lines
for the wind.  
Although plotted against radius, we first calculated $\tau_{2796}$ 
as a function of velocity by summing the opacity in a series of
discrete and small radial intervals
between $r_{\rm inner}$  and $r_{\rm outer}$.   We then mapped
$\tau_{2796}$ onto radius using the radial velocity profile and 
checked that this profile is in good agreement with
the Sobolev approximation.  
The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
is scaled down by the ratio of $f\lambda$ but otherwise identical.  Similarly,
the optical depth profiles for the \feiid\ transitions are
scaled down by $f \lambda$ and the \nfe/\nmg\ ratio.  
The adopted Doppler parameter
(here $b_{\rm turb} = 15 \mkms$) also has a modest impact on the results,
specially at large optical depths.  A larger/smaller
$b$-value would imply ... [FILL IN]
In turn, this would affect the resulting emission profiles.

Because the results are dictated by the $\tau_{2796}$ profile and the
Doppler parameter, the actual dimensions and density of the wind are
essentially unimportant provided they scale together to give the same
$\tau_{2796}$ profile.  Therefore, one may consider our choices for
$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
Nevertheless, we attempted to adopt values for this fiducial model
that some astrophysical motivation.

Using the methodology described in $\S$~\ref{sec:method}, we
propogated photons from the source and through the outflow to an
`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
complex.  Figure~\ref{fig:fiducial_1d} presents the spectrum
that this observer would record with the ``unattenuated'' source flux
normalized to unit value.   The \ion{Mg}{2} profiles
show the canonical `P-Cygni profile' that characterize a continuum
source embedded within an outflow.  Strong absorption is evident at
$v < -50 \mkms$ in both transitions and each shows emission at
positive velocities.  For this isotropic and dust-free model, the
total equivalent width of the doublet must be zero
(Table~\ref{tab:fiducial_EW}), i.e.\ every photon
absorbed still escapes the system, primarily at lower
energies.  The wind simply shuffles photons in frequency space.

Focusing on the \ion{Mg}{2} absorption, one notes the profiles have
positive intensity yet similar depth even though their $f\lambda$
values differ by a factor of two.  In standard absorption line
analysis, this is generally 
the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
saturated) which only partially covers the emitting source
\citep[e.g.][]{hamman10}.  Our fiducial wind model, however, 
{\it entirely} covers the source; the apparent partial covering must
be related to a different effect.
Figure~\ref{fig:noemiss}, which compares the true
absorption profiles against the case where absorbed photons are not
re-emitted, further illustrates this issue.   As expected from the
$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}, the no-emission
case predicts a strong \mgiid\ doublet that absorbs all photons at
$v \approx -100 \mkms$, i.e.\ $I_{2796} = \exp(-\tau_{2796}) \approx 0$.
The actual profile, meanwhile, has been `filled in' at $v \approx -100
\mkms$ by photons scattered and re-emitted by the wind (see below).  An
absorption-line analysis that ignores these effects
\citep[e.g.][]{sato} would systematically underestimate the true optical
depth and falsely conclude partial covering.  We will find that this
behaviour is a generic results for models with a high degree of
isotropy.
[Dan's analytic calculation here? or Appendix?]

One also notes that the emission profiles of the \mgiid\ doublet
are very similar and have comparable equivalent widths.  In fact the
flux of the \mgiib\ transition even exceeds that for \mgiia.  The
emission profiles are similar because the absorption is saturated.
Furthermore, the flux from \mgiib\ is greater than that for
\mgiia\ because the wind speed exceeds the velocity separation
of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$, such
that the \mgiib\ absorption profile partially absorbs the red wing of the
\mgiia\ emission profile.  The relative strengths of the emission
lines, therefore, is sensitive to both the optical depth and velocity
extent of the wind.

Now consider the \ion{Fe}{2} transitions.
The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
majority of the \ion{Fe}{2} UV1 transitions and several are
shown in the velocity plot.  The line
profile for \feiib\ is very similar to those for the \mgiid\ doublet;
one observes strong absorption to negative velocities and strong
emission at $v > 0 \mkms$ producing a P-Cygni profile.  Splitting
the profile at $v = -50 \mkms$, we measure an equivalent width
$W_{2600}^{\rm abs} = 1.16$\AA\ in absorption and $W_{2600}^{\rm em} =
-0.94$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
equivalent width of $W_{2600}^{\rm TOT} \approx 0.22$\AA.  
[Point out that if $\tau_{2600}$ were higher, than the photons would
likely be more trapped and more would come out as 2626.  Also a
v=0km/s component might make quite a difference.]
In contrast, the \feiia\ resonance line shows much weaker emission and
a much higher total equivalent width ($W_{2586}^{\rm TOT} = 0.49$\AA)
even though the line has a $2 \times$ lower $f\lambda$ value.
The difference comes the extra downward transition from the
\zconfig$_{7/2}$ level and (more importantly) that the Einstein A
coefficients  of the non-resonant lines match and even exceed that for
the resonant line.  In the case of \feiib, the
\ion{Fe}{2}~2626 transition 
has an approximately  $4\times$ smaller coefficient than the
resonance line.  Therefore, the majority of photons absorbed at
$\lambda 2600$ are re-emitted with the same energy and only scatter 
in frequency space around the line.  For \feiia, 
the majority of photons absorbed are re-emitted 
as longer wavelength \ion{Fe}{2}~$\lambda 2612$ or $\lambda 2632$
photons.  
The total equivalent width, however, of the lines connected to the
\zconfig$_{7/2}$ upper level does vainsh (i.e.\ photons are conserved
in this fiducial wind).

[Does the FeII 2600 P-Cygni go away if we increase $\tau_{2600}$?]

Our 3D Monte Carlo algorithm tracks the spatial emissivity of the source+wind
complex as a function of frequency.  From this output, we
constructed surface-brightness maps producing a
dataset analagous to intergral-field-unit (IFU) observations.  In
Figure~\ref{fig:fiducial_ifu_mgii}, we present the output for our
fiducial wind model at several velocities relative to the \mgiia\
transition. At $v \le -200 \mkms$, where the wind has an optical
depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
the source contributes significantly to the observed flux.  
At $v=-100 \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely from photons scattered by the wind.  This scattered emission
actually exceeds the source+wind emission at 
$v = -200\mkms$ such
that the absorption profile reaches peak depth at a velocity that is
negatively offset from
the peak in optical depth.  The net result of the scattered photons is
a weaker \ion{Mg}{2} profile that is offset fromt he true optical
depth profile.  Clearly, this will complicate efforts to estimate the
speed, covering fraction, and total column density of the wind.  At $v
= 0 \, \mkms$, the wind and source have comparable total flux and the
latter dominates at higher velocities.  
At $v_{\rm r} \ge 0
\mkms$,  both the source and wind contribute to the observed emission.

@@

Similar characteristics are observed for the \ion{Fe}{2} resonance
transitions (Figure~\ref{fig:fiducial_ifu_feii2600}).
For transitions to fine-structure levels of the \aconfig, the source
is unattenuated but there is also a significant contribution from the
wind (Figure~\ref{fig:fiducial_ifu_feii2612}).
[Show a cut and comment on the fraction of light in 1-3\,kpc, 1-10,
and 1-20; ignoring the source]

@@

\begin{equation}
\mvr = \ltp \frac{A_{\rm LBG}}{1-\alpha} \rtp^{1/2} \ltk r_{\rm
  inner}^{1-\alpha} - r^{1-\alpha} \rtk^{1/2}
\label{eqn:LBG_vlaw}
\end{equation}
with $A_{\rm LBG}$ a constant that sends the terminal speed,
$r_{\inner}$ is the inner radius of the wind (taken to be 1\,kpc) and
$\alpha$ describes how steeply the velocity curve rises.  Their
analysis of the LBG absorption profiles required
a very steeply rising curve with $\alpha \approx 1.3$.
The resulting curve is shown as a dotted line in the top panel of
Figure~\ref{fig:LBG_Sobolev}.

@@

>>>>

\begin{abstract}
\begin{itemize}
\item Emission is a generic feature of (nearly) isotropic winds.  This
  emission fills in absorption at $v \approx 0$, significantly
  complicating the absorption-line analysis, especially of an ISM
  component. 
\end{itemize}
\end{abstract}

@@

In this paper, we will focus on two sets of radiative transitions
associated with the Fe$^+$ and Mg$^+$ ions.
Although a limited
set, the two ions and their transitions are characteristic
of the majority of low-ions 
observed in cool-gas outflows. Therefore, many
of our results can be generalized to studies that focus on other atoms
and ions of cool gas.

The Mg$^+$ ion, with a single 3s electron in the ground-state,
exhibits an alkali doublet of transitions similar to the
\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
we present the energy level diagram for this 
\mgiid\ doublet.  In non-relativistic quantum
mechanics, the 2p$^6$3p level is said to be split by spin-orbit
coupling; this produces the observed line doublet.  These are the only
\ion{Mg}{2} electric-dipole transitions 
with wavelengths near 2800\AA\ and the transtion connecting
the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
selection rules.  Therefore, an absorption from
\maconfig~$\to$~\mbconfig\
is followed essentially 100$\%$ of the time by a spontaneous decay to the
ground state. Our treatment will ignore any other possibilities
(e.g.\ absorption by a second photon when at the \mbconfig\ level).

The physics of the \mgiid\ doublet
is analagous to the physics of \ion{H}{1}
\lya, the \naid\ doublet, and many other doublets commonly
studied in the ISM and IGM.  These doublets differ only in
their wavelengths and the energy of the doublet separation. 
For \ion{H}{1} \lya, the
separation is sufficiently small ($\Delta v = c \Delta E / E \approx
1.3 \mkms$) that most radiative transfer treatments actually ignore that
there are two transitions.   This is generally justifiable
because 
most astrophysical processes have turbulent motions that
significantly exceed this velocity separation and effectively mix the
two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \, \mkms$),  
\ion{Na}{1} ($\Delta v \approx 304 \, \mkms$), and most of the other doublets
commonly studied the separations are large and the lines
must be treated separately.  Regarding analysis of outflows, the line
separation plays an important role when the outflow speed matches or
exceeds $\Delta v$.

Iron exhibits the most complex set of energy levels of the elements
frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
energy levels recorded \citep{iron}, and even this is an
incomplete list.  
One reason for iron's complexity is
that the majority of its configurations exhibit fine-structure splitting.
This includes the ground-state configuration (\aconfig) which is split
into 5 levels with 
excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
$T_{\rm ex} \approx 500-1500$\,K.  These levels are usually labelled by the total angular momentum
$J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
Transitions between these fine-structure levels are 
forbidden (magnetic-dipole) with spontaneous decay times of several hours.

In this paper, we will focus on transitions between the ground-state
configuration and the levels associated with the \zconfig\
configuration.  This set of transitions (named the
UV1 mutliplet) have wavelengths near 2600\AA.
There are two resonance-line transitions\footnote{We adopt the
  convention that a resonance line is connected to the ground-state.} 
associated with this multiplet (\feiid)
corresponding to $\Delta J = 0, -1$.  The solid (green) downward
arrows in Figure~\ref{fig:energy} mark the transitions that connect to
the upper energy levels of the resonance lines.  These transitons can
occur following the absorption of a single photon by Fe$^+$ in its
ground-state.

The Figure also shows (as dashed downward arrows) two of the
transitions that connect to higher energy levels of the \zconfig\
configuration.  Radiatively, these can only occur after the absorption
of two photons: one to raise the electron from the ground-state to an
excited state and one from the excited state to one of the \zconfig\
levels with $J \le 5/2$.  Such excitation by the
absorption of UV photons is termed indirect UV pumping
\citep[e.g][]{sv02,pcb06} and requires the ion to lie
near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
following, we will assume that this does not occur and that only the 
true ground-state is populated by electrons.

Our calculations also ignore collisional
processes\footnote{Recombination is also ignored.}, i.e.\ collisional
excitation and de-excitation of the various levels.  For the
fine-structure levels of the \aconfig\ configuration, the excitation
energies are modest ($T_{\rm ex} \sim 1000$\,K) but the critical
density $n_c$ is very large.  For the \aconfig$_{9/2} \to
$\aconfig$_{7/2}$ transition, the critical density $n_c \approx XX
\cm{-3}$.  At these densities, one would predict significant (and
detectable) quantities of \ion{Fe}{1} which has not yet been observed
\citep[see also][]{pcb06}.  Furthermore, observations rarely show
{\it absorption} from the
fine-structure levels of the \aconfig\ configuration and  none that is
significantly blue-shifted \citep{rubin+10}.
Empirically, collsioinal excitation is insignificant and, by
inference, one may neglect collisional de-excitation.  
For Mg$^+$, $n_c = ??$ and $T_{\rm ex} \approx 50,000$\,K  
implying negligible collsiional excitation for the cool gas.

@@

Nearly all of the absorption studies on cool-gas outflows 
have focused on intensely, star-forming galaxies.  The
intrinsic emisison of these galaxies is a complex combination of
stars and \ion{H}{2} regions that is then modulated by dust and gas
within the galaxy's ISM.  For the spectral regions studied
here, most stars show a featureless continuum with a few spectral
types showing significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
[Any emission??]  \ion{H}{2} regions, meanwhile, are observed to emit
at the \mgiid\ doublet, primarily due to recombinations in the outer
layers [How about FeII?].  It is beyond the scope of this paper to
properly model the 
stellar absorption and \ion{H}{2} region emission, but the reader
should be aware that they can complicate the observed spectrum,
independent of a galactic outflow, especially at $v \approx 0 \mkms$.
In the following, we will simply assume a flat continuum 
normalized to unit value.  The size of the emitting
region $r_{\rm source}$, however, is a variable parameter.

@@

In this section, we explore a simple yet illustrative wind model for
a galactic-scale outflow.  The properties of this wind were tuned, in
part, to yield a \ion{Mg}{2} absorption profile 
similar to that observed toward $z<1$, star-forming galaxies
\citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
favor this fiducial model over any other wind scenario nor do its
properties have spcial physical motivation.
The primary purpose of the fiducial model is to establish a baseline
for discussion.

@@

\begin{equation}
n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2}
\end{equation}
(mass-flux conserving) and a velocity

\begin{equation}
\vec v = v_r (r) \hat r = v_0 r \hat r
\label{eqn:vel}
\end{equation}
which corresponds to a purely radial flow.  Turbulent motions are
characterized by a Doppler parameter $b_{\rm turb}$.  
The wind is isotropic, dust-free, and extends from an inner wind
radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  At
the center of the wind 
is a homogenous source of continuum photons with a size $r_{\rm source}$.  Lastly,
we convert the hydrogen density $n_{\rm H}$ to the number density of
Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
absolute metallicity of 1/2 solar and depletion factors of 1/10 and
1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
and \nfe=\nmg/2.   
All of the parameters are summarized in Table~\ref{tab:fiducial}.

In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
profiles against radius for the fiducial wind model;  
their single power-law expressions are evident.  The figure also
shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
This curve determines the resultant absorption/emission lines
for the wind.  
Although plotted against radius, we first calculated $\tau_{2796}$ 
as a function of velocity by summing the opacity in a series of
discrete and small radial intervals
between $r_{\rm inner}$  and $r_{\rm outer}$.   We then mapped
$\tau_{2796}$ onto radius using the velocity expression
(Equation~\ref{eqn:vel}). 
The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
is scaled down by the ratio of $f\lambda$ but otherwise identical.  Similarly,
the optical depth profiles for the \feiid\ transitions are
scaled down by $f \lambda$ and the \nfe/\nmg\ ratio.  
The adopted Doppler parameter
(here $b_{\rm turb} = 15 \mkms$) also has only a modest impact on the results.
A larger/smaller $b$-value would imply ... [FILL IN]

Because the results are dictated by the $\tau_{2796}$ profile in
velocity space, the actual dimensions and density of the wind are
essentially unimportant provided they scale together to give nearly the same
$\tau_{2796}$ profile.  Therefore, one may consider our choices for
$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
Nevertheless, we adopted values for this fiducial model with
some astrophysical motivation (e.g. values that correspond to
galactic dimensions).

Using the methodology described in $\S$~\ref{sec:method}, we
propogated photons from the source and through the outflow to an
`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
complex.  Figure~\ref{fig:fiducial_1d} presents the spectrum
that this observer would record with the ``unattenuated'' source flux
normalized to unit value.   The \ion{Mg}{2} doublet
shows the canonical `P-Cygni profile' that characterize a continuum
source embedded within an outflow.  Strong absorption is evident at
$v < -50 \mkms$ in both transitions and each shows emission at
positive velocities.  For this isotropic and dust-free model, the
total equivalent width of the doublet must be zero
(Table~\ref{tab:fiducial_EW}), i.e.\ every photon
absorbed eventually escapes the system, generally at lower
energies.  The wind simply shuffles the photons in frequency space.

Focusing on the \ion{Mg}{2} absorption, one notes the profiles have
positive intensity yet similar depth even though their $f\lambda$
values differ by a factor of two.  In standard absorption line
analysis, this is generally 
the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
saturated) which only partially covers the emitting source
\citep[e.g.][]{hamman10}.  Our fiducial wind model, however, 
{\it entirely} covers the source; the apparent partial covering must
be due to a different effect.
Figure~\ref{fig:noemiss}, which compares the true
absorption profiles against the case where absorbed photons are not
re-emitted, further illustrates this issue.   As expected from the
$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}, the no-emission
case predicts a strong \mgiid\ doublet that absorbs all photons at
$v \approx -100 \mkms$, i.e.\ $I_{2796} = \exp(-\tau_{2796}) \approx 0$.
The actual profile, meanwhile, has been `filled in' at $v \approx -100
\mkms$ by photons scattered and re-emitted by the wind (see below).  An
absorption-line analysis that ignores these effects
\citep[e.g.][]{sato} would systematically underestimate the true optical
depth and falsely conclude partial covering.  We will find that this
behaviour is a generic result of wind models, even for cases that are
not fully isotropic.
[Dan's analytic calculation here? or Appendix?]

One also notes that the emission profiles of the \mgiid\ doublet
are very similar with comparable equivalent widths.  In fact the
flux of the \mgiib\ transition even exceeds that for \mgiia, the ratio
is far below the $2:1 f\lambda$ ratio that one might have expected. The
emission profiles are so similar simply because the absorption is
highly saturated.
Furthermore, the flux from \mgiib\ is greater than that for
\mgiia\ because the wind speed exceeds the velocity separation
of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$, such
that the \mgiib\ absorption profile partially absorbs the red wing of the
\mgiia\ emission profile.  The relative strengths of the emission
lines, therefore, is sensitive to both the opacity and velocity
extent of the wind.

Now consider the \ion{Fe}{2} transitions.
The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
majority of the \ion{Fe}{2} UV1 transitions and several are
shown in the velocity plot.  The line
profile for \feiib\ is very similar to those for the \mgiid\ doublet;
one observes strong absorption to negative velocities and strong
emission at $v > 0 \, \mkms$ producing a P-Cygni profile.  Splitting
the profile at $v = -50 \, \mkms$, we measure an equivalent width
$W_{2600}^{\rm abs} = 1.16$\AA\ in absorption and $W_{2600}^{\rm em} =
-0.94$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
equivalent width of $W_{2600}^{\rm TOT} \approx 0.22$\AA.  
[Point out that if $\tau_{2600}$ were higher, than the photons would
likely be more trapped and more would come out as 2626.  Also a
v=0km/s component might make quite a difference. It does!]
In contrast, the \feiia\ resonance line shows much weaker emission and
a much higher total equivalent width ($W_{2586}^{\rm TOT} = 0.49$\AA)
even though the line has a $2 \times$ lower $f\lambda$ value.
This difference is due to the extra downward transition from the
\zconfig$_{7/2}$ level and (more importantly) that the Einstein A
coefficients of the non-resonant lines are comparable to and even
exceed the Einstein A coefficient of
the resonant line.  In the case of \feiib, the
\ion{Fe}{2}~2626 transition 
has an approximately  $4\times$ smaller coefficient than the
resonance line.  Therefore, the majority of photons absorbed at
$\lambda 2600$ are re-emitted with nearly the same energy and only scatter 
in frequency space around the line.  For \feiia, 
the majority of photons absorbed are re-emitted 
as longer wavelength \ion{Fe}{2}$^* \; \lambda 2612$ or $\lambda 2632$
photons.  
The total equivalent width, however, of the lines connected to the
\zconfig$_{7/2}$ upper level must vainsh (i.e.\ photons are conserved
in this fiducial wind).

[Does the FeII 2600 P-Cygni go away if we increase $\tau_{2600}$? It
can]

Our 3D Monte Carlo algorithm tracks the spatial emissivity of the source+wind
complex as a function of frequency.  From this output, we
constructed surface-brightness maps producing a
dataset analagous to intergral-field-unit (IFU) observations.  In
Figure~\ref{fig:fiducial_ifu_mgii}, we present the output for our
fiducial wind model at several velocities relative to the \mgiia\
transition. At $v -200 \, \mkms$, where the wind has an optical
depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
the source contributes significantly to the observed flux.  
At $v=-100 \, \mkms$, however, the
wind absorbs all photons from the source and the observed emission is
entirely from photons scattered by the wind.  This scattered emission
actually exceeds the source+wind emission at 
$v = -200 \, \mkms$ such
that the absorption profile reaches peak depth at a velocity that is
negatively offset from
the peak in optical depth.  The net result of the scattered photons is
a weaker \ion{Mg}{2} profile that is offset from the true optical
depth profile.  Clearly, this complicates estimates of the
speed, covering fraction, and total column density of the wind.  At $v
= 0 \, \mkms$, the wind and source have comparable total flux and the
latter dominates at higher velocities.  
At $v_{\rm r} \ge 0
\mkms$,  both the source and wind contribute to the observed emission.

@@

Similar characteristics are observed for the \ion{Fe}{2} resonance
transitions (Figure~\ref{fig:fiducial_ifu_feii2600}).
For transitions to fine-structure levels of the \aconfig, the source
is unattenuated but there is also a significant contribution from the
wind (Figure~\ref{fig:fiducial_ifu_feii2612}).
[Show a cut and comment on the fraction of light in 1-3\,kpc, 1-10,
and 1-20; ignoring the source] {\bf [Do this!]}

@@

\begin{equation}
\mvr = \ltp \frac{A_{\rm LBG}}{1-\alpha} \rtp^{1/2} \ltk r_{\rm
  inner}^{1-\alpha} - r^{1-\alpha} \rtk^{1/2}
\label{eqn:LBG_vlaw}
\end{equation}
with $A_{\rm LBG}$ a constant that sends the terminal speed,
$r_{inner}$ is the inner radius of the wind (taken to be 1\,kpc) and
$\alpha$ describes how steeply the velocity curve rises.  Their
analysis of the LBG absorption profiles required
a very steeply rising curve with $\alpha \approx 1.3$.
The resulting curve is shown as a dotted line in the top panel of
Figure~\ref{fig:LBG_Sobolev}.

@@

The results of the full calculation are
shown as the black curve in Figure~\ref{fig:LBG_spec}.  The results
are very similar to the Sobolev calculation; scattered photons fill-in
the absorption profiles at $v \approx 0 \mkms$ and yield significant
emission lines at $v \gtrsim 0 \mkms$ in the resonance lines and at
all velocities for the \ion{Fe}{2}$^*$ transitions.  For \feiia,
the majority of absorbed photons have been converted to its
fine-structure counterparts lending to very weak emission at this
transition. In fact the absorption profile very nearly matches the
model without re-emission indicating that this transition well
reproduces the opacity of the wind.  [Could SiII or OI provide a
similar angle?]

[Discuss 'exact' match of Sobolev + Covering at MgII 2796]
[Does the similarity of the two require that the density of clouds
fall off like the Sobolev solution?]

\section{Observables}

Although the focus of this paper is to explore the absorption/emission
profiles for idealized wind models, we ultimately intend to compare 
profiles like these against observations to constrain characteristics
of the wind (e.g.\ raidal extent, energetics).  In this section we
consider a few observables and their dependence on the wind properties.

\subsection{Absorption profiles}

 \begin{enumerate}
   \item Peak optical depth
     \begin{itemize}
       \item Not a robust measure of $\tau_{wind}$
       \item Not even a good relative predictor for $\tau$
       \item Not a robust predictor of $f_c$
     \end{itemize}
   \item Kinematics
     \begin{itemize}
       \item Nearly robust for $v<v_{min}$
       \item But what sets $v_{min}$?
       \item Generally get the full extent of the wind speed
     \end{itemize}
   \item EW
     \begin{itemize}
       \item Primarily set by $v_{min}(\tau \sim 1)$
       \item $f\lambda$ matters, but so do emission channels
     \end{itemize}
   \item Fine-structure
     \begin{itemize}
       \item Distance to the source
     \end{itemize}
 \end{enumerate}

\subsection{Emission profiles}

 \begin{enumerate}
   \item Resonant lines
     \begin{itemize}
       \item Kinematics of backside
       \item Flux + relative
    \end{itemize}
   \item Fine-structure
     \begin{itemize}
       \item Flux $\propto \tau_{wind}$ + relative
       \item Kinematics (anisotropy)
    \end{itemize}
 \end{enumerate}
